Containers and R---the Rockerverse and beyond

### 2019-12-16 manuscript.Rmd
update author list and contributions section

---
title: "Containers and R---the Rockerverse and beyond"
author:
  - name: Daniel Nüst
    affiliation: University of Münster
    address:
      - Institute for Geoinformatics
      - Heisenbergstr. 2
      - 48149 Münster, Germany
      - \orcid{0000-0002-0024-5046}
    email: daniel.nuest@uni-muenster.de
  - name: Carl Boettiger
    #affiliation: -
    #email: -
  - name: Robrecht Cannoodt
    affiliation: Ghent University
    address:
      - Data Mining and Modelling for Biomedicine group
      - VIB Center for Inflammation Research
      - Technologiepark 71
      - 9052 Ghent, Belgium
      - \orcid{0000-0003-3641-729X}
    email: robrecht@cannoodt.dev
  - name: Ellis Hughes
  - name: Dirk Eddelbuettel
    affiliation: University of Illinois at Urbana-Champaign
    address:
      - Department of Statistics
      - Illini Hall, 725 S Wright St
      - Champaign, IL 61820, USA
      - \orcid{0000-0001-6419-907X}
    email: dirkd@eddelbuettel.com
  - name: Mark Edmondson
    affiliation: IIH Nordic A/S, Google Developer Expert for GCP
    email: mark@markedmondson.me
  - name: Colin Fay
    affiliation: ThinkR
    address:
      - 5O rue Arthur Rimbaud
      - 93300 Aubervilliers, France
      - \orcid{0000-0001-7343-1846}
    email: contact@colinfay.me
  - name: Ben Marwick
    #affiliation: -
    #email: -
  - name: Karthik Ram
    affiliation: Berkeley Institute for Data Science
    address:
      - University of California
      - Berkeley, CA 94720, USA
      - \orcid{0000-0002-0233-1757}
    email: karthik.ram@berkeley.edu
  - name: Noam Ross
    affiliation: EcoHealth Alliance
    address:
      - 460 W 34th St., Ste. 1701
      - New York, NY 10001, USA
      - \orcid{0000-0002-0233-1757}
    email: ross@ecohealthalliance.org
  - name: Nan Xiao
    affiliation: Seven Bridges Genomics
    address:
      - 529 Main St, Suite 6610
      - Charlestown, MA 02129, USA
      - \orcid{0000-0002-0250-5673}
    email: me@nanx.me
  - name: Lori Shepherd
    affiliation: Roswell Park Comprehensive Cancer Center
    address:
      - Elm & Carlton Streets
      - Buffalo, New York, 14263, USA
      - \orcid{0000-0002-5910-4010}
    email: lori.shepherd@roswellpark.org
  - name: Nitesh Turaga
    affiliation: Roswell Park Comprehensive Cancer Center
    address:
      - Elm & Carlton Streets
      - Buffalo, New York, 14263, USA
      - \orcid{0000-0002-0224-9817}
    email: nitesh.turaga@roswellpark.org
  - name: Jacqueline Nolis
    affiliation: Nolis, LLC
    address:
      - Seattle, WA, USA
      #- \orcid{NA}
    email: jacqueline@jnolis.com
  - name: Hong Ooi
    affiliation: Microsoft
    address:
    - Level 5, 4 Freshwater Place
    - Southbank, VIC 3006, Australia
    email: hongooi@microsoft.com
abstract: >
  The Rocker project provides widely-used Docker images for R across different application scenarios.
  This articles surveys describe downstream projects building upon Rocker.
  We also look beyond Rocker to other projects connecting containerisation with R.
  These use cases and the diversity of applications demonstrate the power of Rocker and containerisation for collaboration, effectivity, scalability, and transparency.
# blank footnote? https://tex.stackexchange.com/questions/170511/footnotes-without-numbering
output:
  rticles::rjournal_article:
    keep_tex: true
    includes:
      in_header: header.tex
---

@@

## Interfaces for Docker in R [Ellis Hughes, Robrecht Cannoodt]

@@

# Discussion/outlook/conclusion [@all, please add bullet points]

@@

DN conceived of the presented idea and \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team} and wrote the section about images for R distributions.
CB ..
RC and RC wrote the section on interfaces for Docker in R.
DE ..
ME ..
CF wrote the section about `r-online`, `dockerfiler`, `r-ci` and `r-db`.
BW ..
KR ..
NR ..
NX wrote the section on liftr.
LS \& NT wrote the section on Bioconductor.
All authors contributed to the discussion and outlook section and approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page}, \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history}, and \href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues} provide a detailed view on the respective contributions.

>>>>

---
title: "Containers and R---the Rockerverse and beyond"
author:
  - name: Daniel Nüst
    # https://github.com/nuest
    affiliation: University of Münster
    address:
      - Institute for Geoinformatics
      - Heisenbergstr. 2
      - 48149 Münster, Germany
      - \orcid{0000-0002-0024-5046}
    email: daniel.nuest@uni-muenster.de
  - name: Robrecht Cannoodt
    # https://github.com/rcannood
    affiliation: Ghent University
    address:
      - Data Mining and Modelling for Biomedicine group
      - VIB Center for Inflammation Research
      - Technologiepark 71
      - 9052 Ghent, Belgium
      - \orcid{0000-0003-3641-729X}
    email: robrecht@cannoodt.dev
  - name: Dirk Eddelbuettel
    # https://github.com/eddelbuettel
    affiliation: University of Illinois at Urbana-Champaign
    address:
      - Department of Statistics
      - Illini Hall, 725 S Wright St
      - Champaign, IL 61820, USA
      - \orcid{0000-0001-6419-907X}
    email: dirkd@eddelbuettel.com
  - name: Mark Edmondson
    affiliation: IIH Nordic A/S, Google Developer Expert for GCP
    email: mark@markedmondson.me
  - name: Colin Fay
    # https://github.com/ColinFay
    affiliation: ThinkR
    address:
      - 5O rue Arthur Rimbaud
      - 93300 Aubervilliers, France
      - \orcid{0000-0001-7343-1846}
    email: contact@colinfay.me
  - name: Karthik Ram
    # https://github.com/karthik
    affiliation: Berkeley Institute for Data Science
    address:
      - University of California
      - Berkeley, CA 94720, USA
      - \orcid{0000-0002-0233-1757}
    email: karthik.ram@berkeley.edu
  - name: Noam Ross
    # https://github.com/noamross
    affiliation: EcoHealth Alliance
    address:
      - 460 W 34th St., Ste. 1701
      - New York, NY 10001, USA
      - \orcid{0000-0002-0233-1757}
    email: ross@ecohealthalliance.org
  - name: Nan Xiao
    # https://github.com/nanxstats
    affiliation: Seven Bridges Genomics
    address:
      - 529 Main St, Suite 6610
      - Charlestown, MA 02129, USA
      - \orcid{0000-0002-0250-5673}
    email: me@nanx.me
  - name: Lori Shepherd
    # https://github.com/lshep
    affiliation: Roswell Park Comprehensive Cancer Center
    address:
      - Elm & Carlton Streets
      - Buffalo, New York, 14263, USA
      - \orcid{0000-0002-5910-4010}
    email: lori.shepherd@roswellpark.org
  - name: Nitesh Turaga
    # https://github.com/nturaga
    affiliation: Roswell Park Comprehensive Cancer Center
    address:
      - Elm & Carlton Streets
      - Buffalo, New York, 14263, USA
      - \orcid{0000-0002-0224-9817}
    email: nitesh.turaga@roswellpark.org
  - name: Jacqueline Nolis
    # https://github.com/jnolis/
    affiliation: Nolis, LLC
    address:
      - Seattle, WA, USA
      #- \orcid{NA}
    email: jacqueline@jnolis.com
  - name: Hong Ooi
    # https://github.com/Hong-Revo
    affiliation: Microsoft
    address:
    - Level 5, 4 Freshwater Place
    - Southbank, VIC 3006, Australia
    email: hongooi@microsoft.com
  - name: Ellis Hughes
    # https://github.com/thebioengineer
    affiliation: Fred Hutchinson Cancer Research Center 
    address:
      - Vaccine and Infectious Disease
      - 1100 Fairview Ave. N., P.O. Box 19024
      - Seattle, WA 98109-1024, USA
      #- \orcid{}
    email: ehhughes@fredhutch.org
  - name: Ben Marwick
abstract: >
  The Rocker project provides widely-used Docker images for R across different application scenarios.
  This articles surveys describe downstream projects building upon Rocker.
  We also look beyond Rocker to other projects connecting containerisation with R.
  These use cases and the diversity of applications demonstrate the power of Rocker and containerisation for collaboration, effectivity, scalability, and transparency.
# blank footnote? https://tex.stackexchange.com/questions/170511/footnotes-without-numbering
output:
  rticles::rjournal_article:
    keep_tex: true
    includes:
      in_header: header.tex
---

@@

## Interfaces for Docker in R

@@

# Conclusions

@@

DN conceived of the presented idea and \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}, wrote the section about images for R distributions, wrote the conclusions section, and revised all sections.
CB ..
RC and EH wrote the section on interfaces for Docker in R.
DE wrote the introduction and section about Rocker.
ME ..
CF wrote the paragraphs about `r-online`, `dockerfiler`, `r-ci` and `r-db`.
BW ..
KR ..
NR ..
NX wrote the section on liftr.
LS \& NT wrote the section on Bioconductor.
All authors contributed minor edits, gave feedback on other sections, and approved the final version.

This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page}, \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history}, and \href{https://github.com/nuest/rockerverse-paper/issues/}{discussion issues} provide a detailed view on the respective contributions.
